{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-26 thesis/landslide.tex
consistency of preempt-everywhere and maximal state space modes decapitalized

\begin{itemize}
	\item {\tt -C}: enable ``control experiment'' mode, i.e., run only 1 instance of Landslide, with all (non-data-race) preemption points enabled in advance
	\item {\tt -I}: enable Iterative Context Bounding (requires {\tt -C}, although future work may relax this restriction);
		this generally causes bugs to be found faster should they exist, but degrades completion time
		(\cref{sec:landslide-icb})
	\item {\tt -0}: enable Preempt-Everywhere mode
		(\cref{sec:quicksand-impl-modes}, \cref{sec:quicksand-impl-landslide}, requires {\tt -C})
	\item {\tt -M}: enable Maximal State Space mode,
		which prioritizes the maximal state space to optimize for fast verification,
		abandoning all subset jobs even if they might find bugs faster
		(\cref{sec:tm-eval}, incompatible with {\tt -C}).
		According to \cref{sec:quicksand-soundness}'s soundness proofs,
		this is equivalent to {\tt -0}
		(and according to my experience, \revisionminor{much} faster as well).
	\item {\tt -H}: use Limited Happens-Before for data race analysis (\cref{sec:background-hb})
		(default for Pebbles kernelspace mode)
	\item {\tt -V}: use vector-clock-based Pure Happens-Before for data race analysis (\cref{sec:background-hb})
		(default for P2/PSU userspace and Pintos modes)
	\item {\tt -X}: support transactional memory (\Cref{chap:tm})
	\item {\tt -A}: support multiple abort codes during transaction failure (\cref{sec:tm-implementation});
		required for testing programs which behave differently under different abort circumstances,
		but impacts the state space size
	\item {\tt -S}: suppress retry aborts during transaction failure (\cref{sec:tm-implementation})
	\item {\tt -R}: enable retry-set state space reduction for transactional tests (\cref{sec:tm-implementation})
	\item {\tt -P}: support Pintos architecture (enabled automatically when {\tt pintos-setup.sh} is run)
	\item {\tt -4}: support Pebbles architecture (enabled automatically when either {\tt p2-setup.sh} or {\tt psu-setup.sh} is run)
	\item {\tt -e ETAFACTOR}: configure heuristic state space ETA deferring factor (\cref{sec:quicksand-id}; described in detail in {\tt id/option.c})
	\item {\tt -E ETATHRESH}: configure heuristic threshold of state space progress for judging ETA stability (\cref{sec:quicksand-id}; described in detail in {\tt id/option.c})
\end{itemize}

@@

\begin{enumerate}
\item {\bf Search algorithm options}
\begin{itemize}
	\item {\tt ICB=0} - enable Iterative Context Bounding (\cref{sec:landslide-icb});
		corresponds to {\tt -I} in \cref{sec:landslide-quicksand-options}.
	\item {\tt PREEMPT\_EVERYWHERE=0} - enable Preempt-Everywhere mode (\cref{sec:quicksand-eval});
		corresponds to {\tt -0} in \cref{sec:landslide-quicksand-options}.
	\item {\tt EXPLORE\_BACKWARDS=0} - configure whether, at each newly encountered preemption point,
		to allow the current thread to run first then later upon backtracking to preempt (0),
		or to issue preemptions first and then try continuing the current thread later (1).
		0 tends to produce shorter preemption traces while 1 tends to find bugs faster (\cite[\S{}8.7.1]{landslide}).
		Not compatible with ICB.
\end{itemize}

@@

In Preempt-Everywhere mode, Landslide instead marks all shared memory accesses
as long as they are not part of either the mutex implementation or the running thread's stack frame.
The {\tt data\_race} command is ignored and {\tt suspected\_data\_race()}
instead checks whether the instruction pointer is associated with any such shared memory access.

>>>>

\begin{itemize}
	\item {\tt -C}: enable ``control experiment'' mode, i.e., run only 1 instance of Landslide, with all (non-data-race) preemption points enabled in advance
	\item {\tt -I}: enable Iterative Context Bounding (requires {\tt -C}, although future work may relax this restriction);
		this generally causes bugs to be found faster should they exist, but degrades completion time
		(\cref{sec:landslide-icb})
	\item {\tt -0}: enable preempt-everywhere mode
		(\cref{sec:quicksand-impl-modes}, \cref{sec:quicksand-impl-landslide}, requires {\tt -C})
	\item {\tt -M}: enable maximal state space mode,
		which prioritizes the maximal state space to optimize for fast verification,
		abandoning all subset jobs even if they might find bugs faster
		(\cref{sec:tm-eval}, incompatible with {\tt -C}).
		According to \cref{sec:quicksand-soundness}'s soundness proofs,
		this is equivalent to {\tt -0}
		(and according to my experience, \revisionminor{much} faster as well).
	\item {\tt -H}: use Limited Happens-Before for data race analysis (\cref{sec:background-hb})
		(default for Pebbles kernelspace mode)
	\item {\tt -V}: use vector-clock-based Pure Happens-Before for data race analysis (\cref{sec:background-hb})
		(default for P2/PSU userspace and Pintos modes)
	\item {\tt -X}: support transactional memory (\Cref{chap:tm})
	\item {\tt -A}: support multiple abort codes during transaction failure (\cref{sec:tm-implementation});
		required for testing programs which behave differently under different abort circumstances,
		but impacts the state space size
	\item {\tt -S}: suppress retry aborts during transaction failure (\cref{sec:tm-implementation})
	\item {\tt -R}: enable retry-set state space reduction for transactional tests (\cref{sec:tm-implementation})
	\item {\tt -P}: support Pintos architecture (enabled automatically when {\tt pintos-setup.sh} is run)
	\item {\tt -4}: support Pebbles architecture (enabled automatically when either {\tt p2-setup.sh} or {\tt psu-setup.sh} is run)
	\item {\tt -e ETAFACTOR}: configure heuristic state space ETA deferring factor (\cref{sec:quicksand-id}; described in detail in {\tt id/option.c})
	\item {\tt -E ETATHRESH}: configure heuristic threshold of state space progress for judging ETA stability (\cref{sec:quicksand-id}; described in detail in {\tt id/option.c})
\end{itemize}

@@

\begin{enumerate}
\item {\bf Search algorithm options}
\begin{itemize}
	\item {\tt ICB=0} - enable Iterative Context Bounding (\cref{sec:landslide-icb});
		corresponds to {\tt -I} in \cref{sec:landslide-quicksand-options}.
	\item {\tt PREEMPT\_EVERYWHERE=0} - enable preempt-everywhere mode (\cref{sec:quicksand-eval});
		corresponds to {\tt -0} in \cref{sec:landslide-quicksand-options}.
	\item {\tt EXPLORE\_BACKWARDS=0} - configure whether, at each newly encountered preemption point,
		to allow the current thread to run first then later upon backtracking to preempt (0),
		or to issue preemptions first and then try continuing the current thread later (1).
		0 tends to produce shorter preemption traces while 1 tends to find bugs faster (\cite[\S{}8.7.1]{landslide}).
		Not compatible with ICB.
\end{itemize}

@@

In preempt-everywhere mode, Landslide instead marks all shared memory accesses
as long as they are not part of either the mutex implementation or the running thread's stack frame.
The {\tt data\_race} command is ignored and {\tt suspected\_data\_race()}
instead checks whether the instruction pointer is associated with any such shared memory access.
